---
title: "Indonesia - Area inquiry vs. GPS analysis, Exploratory Analysis"
author: "Michael Rahija"
date: "1 March 2016"
output: pdf_document
---

# Details of Sample in Gunung Kidul

```{r, echo = FALSE, message = FALSE, include = FALSE}
#---Import data
library(dplyr)
library(ggplot2)
library(tidyr)
library(plyr)


#Set working directory
sys <- Sys.info()
if(sys[5] == "x86_64"){
  wdir = "~/Dropbox/CROP/Indonesia/cropIndo" #Mac
  dd = "~/Dropbox/CROP/Indonesia/area_data"
} else {
  wdir = "C:/Users/rahija/Dropbox/CROP/Indonesia/cropIndo"
  dd = "C:/Users/rahija/Dropbox/CROP/Indonesia/area_data"
}

#set working directory
setwd(wdir)

dd.files <- list.files(dd, pattern = ".tab")

intActions <- grepl(dd.files, pattern = "interview_actions")
dd.files <- dd.files[!intActions]

###----Take first file ""Cat 3_QUES 3_Crop area by_inquiry_GPS_Indonesia_Iswadi.tab"

id <- grepl(dd.files, pattern = "GPS_Indonesia")

df <- read.table(paste0(dd,"/", dd.files[id]), 
                  sep="\t",
                  header = TRUE,
                  stringsAsFactors = FALSE)
```

The total number of households surveyed was `r nrow(df)`. These households owned  `r sum(df$no_parcels3, na.rm = TRUE)` parcels and had an average number of  `r mean(as.numeric(df$tot_family_member3), na.rm = TRUE)` family members. On average, 
 `r mean(as.numeric(df$active_family_member3), na.rm = TRUE)` family members were involved in agricultural. 
 
The number of households sampled to receive both farmer inquiry and gps area measures were  `r nrow(filter(df, subsample_no == 2))`.

The histogram has a comparision in the distribution of parcel sizes comparing area measure with GPS (area_gps1, area_gps2), and farmer inquiry (area_inquiry). The distribution for area_inquiry seems to be slightly to the right and infact the mean of the farmer inquiry variable is slightly to the right.

```{r, echo = FALSE, message = FALSE}
##---Take parcel roster
id <- grepl(dd.files, pattern = "parcel_roster")

df.pr <- read.table(paste0(dd,"/", dd.files[id]), 
                 sep="\t",
                 header = TRUE,
                 stringsAsFactors = FALSE)

##GPS Analysis


gps <- select(df.pr, area_inquiry, area_gps1, area_gps2)
gps$parcelno <- 1:nrow(gps)
gps <- filter(gps, !is.na(area_gps1))

gps <- select(gps, parcelno, area_inquiry, area_gps1, area_gps2)
#gps$avg_gps <- (gps$area_gps1 + gps$area_gps2)/2

gps.long <- gps %>% 
          gather(measure, size, area_inquiry, area_gps1, area_gps2)

gps.temp <- filter(gps.long, measure %in% c("area_inquiry", "avg_gps"))

cdat <- ddply(gps.long, "measure",summarise, size.mean = mean(size))

ggplot(gps.long, aes(x = size, fill = measure)) +
       geom_density(alpha = .3) +
       ggtitle(paste0("Number of parcels = ", ... =   length(unique(gps.long$parcelno)))) +
  geom_vline(data = cdat, aes(xintercept = size.mean, color = measure),
              size = 1)     +
  annotate("text", label = "Averages of distributions", y = .0011, x = 4000, 
           color = "red") 

```

The dispersion of the farmer inquiry variable is wider than the GPS measures. 

```{r, echo = FALSE, message = FALSE}
ggplot(gps.long, aes(factor(measure), size, fill = factor(measure))) +
  geom_violin()
    
```

# Relationship between farmer inquiry and average gps measure

There is strong positive correlation between the average gps area measure and results from farmer inquiry. 

```{r, echo = FALSE, message = FALSE}
gps$gpsAvg <- (gps$area_gps1 + gps$area_gps2)/2
gps$diff <- abs(gps$area_inquiry - gps$gpsAvg)
gps$perDiff <- abs(gps$diff/((gps$area_inquiry + gps$gpsAvg)/2))

gps <- filter(gps, gpsAvg < 10000)

model <- lm(gpsAvg ~ area_inquiry, data = gps)

ggplot(gps, aes(x = area_inquiry, y = gpsAvg)) +
  geom_point() +
#   geom_abline(intercept = 0, slope = 1, color = "red") +
#   annotate("text", label = "Slope = 1", y = 4500, x = 4000, 
#            color = "red", size= 3) +
  ylim(0,5000) +
  xlim(0,5000) +
  geom_smooth(method=lm, formula=y~x) +
  annotate("text", label = paste0("Coeff = ",format(round(model$coefficients,2)), " ,","\n",
                                  "R-squared = ",format(round(summary(model)$r.squared,2)) ), 
                    y = 2500, x = 4000,color = "blue", size= 3)
```

The *percentage difference* between the average gps measure, and area given by farmer inquiry was computed. The graph below signals that there is a slight negative relationship. In other words, as the plot size increases, the percentage difference between the gps area measure and the area obtained through farmer inquiry decreases.


```{r, echo = FALSE, message = FALSE}
ggplot(gps, aes(x= area_inquiry, y = perDiff)) +
         geom_point() +
         geom_smooth(method = lm) +
         ylab("Percentage Difference") +
         xlab("Area given by farmer inquiry")
```

Since 90% of the plots are less than 2500 meters, let's compare the distributions of the three methods for just these smaller plots. 

# Distribution of plot sizes less than 2500 meters
The vertical lines show the means of the distributions. There seems to be slight upward biase for with the farmer inquiry method.

Also, the violen chart indicates that the disbursion of measurements taken with the gps unit is much wider than famrer inquiry.

```{r, echo = FALSE, message = FALSE}
gps.long <- filter(gps.long, size < 2500)


cdat <- ddply(gps.long, "measure",summarise, size.mean = mean(size))

ggplot(gps.long, aes(x = size, fill = measure)) +
   geom_density(alpha = .3) +
   geom_vline(data = cdat, aes(xintercept = size.mean, color = measure),
              size = 1)     +
  annotate("text", label = "Averages of distributions", y = .0011, x = 1100, 
           color = "red") +
  ggtitle(paste0("Number of parcels = ", length(unique(gps.long$parcelno))))


ggplot(gps.long, aes(factor(measure), size, fill = factor(measure))) +
  geom_violin()
    
```


# Compare average of gps measures to farmer inquiry
```{r, echo = FALSE, message = FALSE}
gps$avg_gps <- (gps$area_gps1 + gps$area_gps2)/2

ggplot(gps, aes(x = area_inquiry, y = avg_gps)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1)

```

# Difference analysis
```{r, echo = FALSE, message = FALSE}
gps$gpsAvg <- (gps$area_gps1 + gps$area_gps2)/2
gps$diff <- abs(gps$area_inquiry - gps$gpsAvg)
gps$perDiff <- abs(gps$diff/((gps$area_inquiry + gps$gpsAvg)/2))
ggplot(gps, aes(x= perDiff, y = area_inquiry)) +
         geom_point()

gps.trunc <- filter(gps, area_inquiry < 14000)
ggplot(gps.trunc, aes(x= perDiff, y = area_inquiry)) +
         geom_point()+
         geom_smooth()

ggplot(gps.trunc, aes(x= gpsAvg, y = perDiff)) +
         geom_point()+
         geom_smooth(method = "lm")

```


###Create graph w/ avgGps and inquiry, run regression line w/ intercept of zero. Then test slope if line is significantly different from 1. 