---
title: "Analyze GPS"
author: "Michael Rahija"
date: "December 1, 2015"
output: pdf_document
---


```{r, echo = FALSE, warning = FALSE, cache = FALSE, include = FALSE}
library(dplyr)
library(reshape)
library(xlsx)
library(ggplot2)
library(ggmap)

#Set working directory
sys <- Sys.info()
if(sys[5] == "x86_64"){
    wdir = "~/Dropbox/CROP/Indonesia/cropIndo" #Mac
    dd = "~/Dropbox/CROP/Indonesia/listing_data/"
    hhdir = "~/Dropbox/CROP/Indonesia/hh_coordinates"
    sdir = "~/Dropbox/CROP/Indonesia/shape_files"
  } else {
    wdir = "C:/Users/rahija/Dropbox/Tanzania_Vet_Services_Project/Live_data_collection/Metadata_reporting/program"
    mdir = "C:/Users/rahija/Dropbox/Tanzania_Vet_Services_Project/Live_data_collection/"
  }

#set working directory
setwd(wdir)


```

A quick look at some completed questionnaires from the first day of listing showed terrible GPS accuracy on many interviews as the first plot below shows. Many interviews had gps accuracy of more than 1.5 kilometers. 
```{r, message = FALSE}
source("R/mergeListing.R")
data <- mergeListing(dd = "~/Dropbox/CROP/Indonesia/")

gps1 <- data.frame(gps = data$gps1_Accuracy, 
                   measure = rep("measure1",n = nrow(data$gps1_Accuracy)))
gps2 <- data.frame(gps = data$gps2_Accuracy, 
                   measure = rep("measure2",n = nrow(data$gps2_Accuracy)))

gps <- rbind(gps1,gps2)


ggplot(gps,aes(x=gps)) + 
    geom_histogram(data=subset(gps,measure == 'measure1'),fill = "red", alpha = 0.2) +
    geom_histogram(data=subset(gps,measure == 'measure2'),fill = "green", alpha = 0.2)
```

Thinking the accuracy might vary by sub-district and census block, I created the plots below. It's clear that there's variation across the areas. Specifically, **Semanu - 009B and Gedang_sari - 015B** seem to have the worst accuracy. 
```{r, message = FALSE, warning = FALSE}
source("R/labelFactors.R")
data <- labelFactors(df = data, 
                     vars = c("sub_dist_name2","census_block"))

#take most accurate gps reading from each survey
if(data$gps1_Accuracy > data$gps2_Accuracy){
  data$gps_Accuracy <- data$gps2_Accuracy
} else {
  data$gps_Accuracy <- data$gps1_Accuracy
  }

ggplot(data, aes(gps_Accuracy)) + 
  geom_histogram(aes(y = ..density..)) + 
  facet_grid(censusBlockLabels~subDistrictNames)
```

Now, let's see if it's a specific enumerator or more than one. 
```{r, message = FALSE, warning = FALSE, echo = FALSE}
#ID actions files
  files = list.files(dd, pattern = "actions")

  data.list <- list()

  #Accumulate actions data in a list
  for (i in 1:length(files)){
    data.temp <- read.delim(paste0(dd,"/",files[i]), header = TRUE,
                            stringsAsFactors = FALSE)
  
    data.list[[i]] <- data.temp 
  }

  #Merge list into one data frame
  datai <- do.call("rbind", data.list)
  datai <- unique(datai)
  
  datai <- filter(datai, Action == "FirstAnswerSet")
  datai <- select(datai,InterviewId,Originator)
  colnames(datai) <- c("physicalBuildingId","Enumerator")
  
  temp <- merge(data,datai, by = "physicalBuildingId")
```

From the plot below, it seems **Margiyana in Gedang Sari, Istono also in Gedang Sari, and Sekar in Semanu** have the worst GPS readings. **Please call these enumerators and make sure they're not taking the GPS reading inside the dwelling. Also, we need to make a mental note that GPS coverage isn't very good in Gedang Sari**
```{r, message = FALSE, warning = FALSE}
ggplot(temp, aes(gps_Accuracy)) + 
  geom_histogram(aes(y = ..density..)) + 
  facet_wrap(Enumerator~subDistrictNames)

```